### 2014-03-15 src/discussion.Rnw
Add more meat to discussion

From our data, we see that for original and generated test suites, the
mutant reduction ratio and standard deviation was similar for stable strategies
(where the standard deviation of the reduction achieved was less than half
of the reduction achieved). This suggests that our analysis is equally
applicable for both generated test suites and original test suites.

Analysing the scores achieved further, we note that the accuracy of prediction
($R^2$) achieved by sampling is generally lower for generated test
suites. Especially, as the fraction of sampling becomes larger the accuracy
reduces drastically for generated test suites while the accuracy still
holds good for original test suites
Secondly, we also observe that the multiplier factor $\beta_1$ 
is smaller for generated test suites than original test suites. This
observation holds good for all sampling and operator selection strategies
examined.  Both these factors together suggest that generated
test suites have a higher variability in their sampled mutation scores than
original test suites. We note that since $\beta_1$ was generally smaller
for generated test suites than original test suites, the full mutation score
corresponding to a sampled mutation score for generated test suites would
be lower than what would be expected from original test suite.
Secondly, the amount of reduction that can be gained by sampling satisfying
a given accuracy is lower for generated test suites in comparison with original
test suites.

>>>>

% About Randoop and Original
From our data, we see that for original and generated test suites, the
mutant reduction ratio and standard deviation was similar for stable strategies
(where the standard deviation of the reduction achieved was less than half
of the reduction achieved). This suggests that our analysis is equally
applicable for both generated test suites and original test suites.

% About Randoop and Original
Analysing the scores achieved further, we note that the accuracy of prediction
($R^2$) achieved by sampling is generally lower for generated test
suites. Especially, as the fraction of sampling becomes larger the accuracy
reduces drastically for generated test suites while the accuracy still
holds good for original test suites
Secondly, we also observe that the multiplier factor $\beta_1$ 
is smaller for generated test suites than original test suites. This
observation holds good for all sampling and operator selection strategies
examined.  Both these factors together suggest that generated
test suites have a higher variability in their sampled mutation scores than
original test suites. We note that since $\beta_1$ was generally smaller
for generated test suites than original test suites, the full mutation score
corresponding to a sampled mutation score for generated test suites would
be lower than what would be expected from original test suite.
Secondly, the amount of reduction that can be gained by sampling satisfying
a given accuracy is lower for generated test suites in comparison with original
test suites.

% Different sampling strategies
Considering different sampling strategies, based on their stability and mutation
reduction achieved, we note that using simple sampling (\textit{sample(x)})
produced the most stable results. For both generated and original test suites,
this strategy produced valid results for all different scopes and sampling
ratios. It also was able to achieve the highest mutation reduction of $72.63$,
that is only $1.37\%$ of the original mutants is needed to produce a highly
accurate ($R^2 = 0.97$) mutation score, with minimal deviation
($\sigma = 6.36$) for original test suites. While the accuracy suffers for
generated test suites it is still high at $R^2 = 0.90$

Considering \textit{round(x)}, the strategy of ignoring low complexity elements
did not pay off, with the scope line having a tendency to become unstable and
inaccurate at high sampling ratios. At very high sampling ratio $1/64$, the
strategy with method scope also becomes unstable and inaccurate. On the whole
\textit{round(x)} did not perform as well as \textit{sample(x)}

The strategy of \textit{ceil(x)} did not perform well either. While the
results were generally stable, the reduction ratios achieved was lower than
\textit{sample(x)}, with similar accuracy.

For line count strategies, only the external sampling produced consistent
results, which was again not as good as \textit{round(x)} for similar mutation
reduction ratios. Secondly, we had hypothesised that perhaps coverage was
a significant contributor to the accuracy of sampled mutation score. However
we could find no evidence in support of this hypothesis with line, method,
class, and project showing similar accuracy and consistency at similar reduction
ratios.

The one per element strategy did not have stable results in general except
for at the scope of line (at which point it was same as count per element
strategy).

Considering mutation operators, only three operators \textit{NC,RC,DC} had
consistent results (and only for original test suites). On considering
operator selection, n-selection strategy had high accuracy and consistency
(though low reduction ratio) until 7-selection (removing seven most numerous
operators) for both generated and original test suites. Javalanche did not
have a high mutation reduction ratio, though it had high accuracy for both
kinds of test suites. The other operator selection methods performed poorly
on generated test suites, while they had high accuracy and reasonable
stability on original test suites. However, for comparable mutation
reduction, they performed worse than random sampling strategies.
